---
title: cityseerr
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r setup, eval=FALSE}
# Install cityseerr from GitHub
# install.packages("pak")
pak::pak("Robinlovelace/cityseerr")
```

# cityseerr

The goal of cityseerr is to provide R bindings to cityseer for computing network centrality, accessibility metrics, and land use analysis on urban street networks.

## Installation

You can install the development version of cityseerr from [GitHub](https://github.com/Robinlovelace/cityseerr) with:

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("Robinlovelace/cityseerr")
```

## Local development

To develop the R package, clone the repo and run:

```{r, eval=FALSE}
devtools::load_all()
```

## Quick test

This test verifies that the Rust code compiles and the basic functions work:

```{r test}
library(cityseerr)

# Create simple test network (in practice, load from file)
nodes_test <- data.frame(
  id = 1:4,
  x = c(0, 1, 1, 2),
  y = c(0, 0, 1, 1)
)

# Test that init_network works
network <- init_network(nodes_test, nodes_test)
print(network)

# Test that compute_centrality_ works
result <- compute_centrality_(network, distances = c(400, 800), betas = c(0.01, 0.005), type = "closeness")
print(result)
```

## Next steps

This is a proof-of-concept package. The next steps are:

1. Test the full build process with `R CMD build cityseerr`
2. Fix any compilation issues
3. Publish to GitHub
4. Open an issue on cityseer asking about R integration

## Contributing

Contributions are welcome! Please see the GitHub repository for details.
